Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-04-23 sattose/paper.tex
Made some stubs for chapters

\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages}

@@

\subsubsection{Our measurements}
We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
\begin{itemize}
  \item We consider clone classes rather than clone pairs
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
\end{itemize}

@@

\subsection{Clone instance contents}
Finally, we looked at the contents of individual clone instances: what  kind of

>>>>

\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages\\- Work in Progress -}

@@

\subsubsection{Our measurements}
We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
\begin{itemize}
  \item We consider clone classes rather than clone pairs
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they use a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
\end{itemize}

@@

\subsection{Clone instance contents}
Finally, we looked at the contents of individual clone instances: what kind of declarations and statements do they span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item
\end{enumerate}

\section{Merging duplicate code through refactoring}
Now we have mapped the contexts in which clones occur, we can start looking at refactoring opportunities. Regarding refactoring, we separate clones in two categories: easy and difficult refactoring opportunities. Easy refactoring opportunities are clones that can easily be automatically refactored. Examples of these opportunities are fully cloned methods or a set of fully cloned statements. According to the relation between the clone instances, we can propose a refactoring automatically.

However, not always can a clone easily be merged. Sometimes a clone spans a statement partially (like a for-loop of which only it's declaration and a part of the body is cloned). Merging the clones can be harder in such instances. Also, cloned code can contain a complex control structure, like labels, return, break, continue, etc. In such instances, more conditions apply do be able to conduct a refactoring, if advisable at all.

\section{Conclusion and next steps}
Next step: build the model to automatically refactor!
